\begin{quote}\textit{
	``It seems that the people registered for the class and the people showing up for class are disjoint.''
}\end{quote}
Today, we will give one or two proofs of Theorem~\ref{smith}: let $G$ be a finite $p$-group, $X$ be a
finite-dimensional $G$-CW complex such that as a topological space, $X$ is an $\F_p$-cohomology sphere (i.e.\ as
graded abelian groups, $H^*(X;\F_p)\cong H^*(S^n;\F_p)$). Then, either $X^G = \varnothing$, or $H^*(X^G;\F_p)\cong
H^*(S^m;\F_p)$ as graded abelian groups, for some $m\le\dim X$. We'll try to be consistent with the notation
in~\cite{MaySmithTheory, AlaskaNotes}.
\begin{proof}[Proof of Theorem~\ref{smith}]
First, we can quickly reduce to the case where $G = \Z/p$: if $H\subset G$ is a normal subgroup, then $X^G\cong
(X^H)^{G/H}$, so you can induct on the order of the group using the Sylow theorems. Thus, we will assume $G =
\Z/p$, whose orbit category is simple:
\[\xymatrix{
	\bullet\ar@(ul, ur)^g\ar[d]\\
	\bullet
}\]
There is a cofiber sequence
\[\xymatrix{
	X_+^G\ar[r] & X_+\ar[r] & X/X^G,
}\]
which is not particularly deep. We're going to construct three special coefficient systems $L$, $M$, and $N$ such
that
\begin{align*}
	H_G^*(X;L) &\cong \wH^*((X/X^G)/G; \F_p)\\
	H_G^*(X;M) &\cong H^*(X;\F_p)\\
	H_G^*(X;N) &\cong H^*(X^G;\F_p).
\end{align*}
These will fit into exact sequences which will imply the inequalities we wanted.

How to we construct custom coefficient systems? Since these constructions commute with colimits, it suffices to
determine them via computation at $n = 0$ and $X = G/H$ for subgroups $H\subset G$, meaning just $e$ and $G$.

For $L$, we want to recover $\wH^0((X/X^G)/G;\F_p)$ for $X = G/e$ and $X = G/G$.
\begin{itemize}
	\item For $X = G/e$, we want $\wH^0((G/\varnothing)/G;\F_p)\cong \wH^0(G_+/G)\cong\F_p$.
	\item For $X = G/G$, we get $\wH^0((*/*)/G;\F_p) = 0$.
\end{itemize}
So we conclude $L(G/e) = \F_p$ and $L(G/G) = 0$.

For $M$, a similar calculation shows we need $H^0(G/e)\cong\F_p[G]$\footnote{Here, $\F_p[G]$ is the \term{group
ring}, the $\F_p$-algebra of functions $G\to\F_p$ with addition taken pointwise and multiplication determined by
requiring $\delta_g\cdot\delta_h = \delta_{gh}$, where $\delta_g$ is a delta function, equal to $1$ at $g$ and $0$
elsewhere.} and $H^0(G/G) = \F_p$, and for $N$, we need $N(G/e) = 0$ and $N(G/G)\cong\F_p$.
\begin{rem}
Almost everything in this proof generalizes; we will only need $X$ to be an $\F_p$-cohomology sphere in order to
know dimensions of a few things. But this technique of customized coefficient systems can be used elsewhere.
\end{rem}
Let $I$ denote the \term{augmentation ideal} of $\F_p[G]$, i.e. the kernel of the map $\F_p[G]\to\F_p$ sending all
$g\mapsto 1$. We will let $I^n$ refer to the coefficient system which assigns $I^n$ to $G/e$ and $0$ to $G/G$.

As coefficient systems, $M/I\cong\F_p$, and therefore there is a short exact sequence of coefficient systems
\[\shortexact{I}{M}{N\oplus L}.\]
This implies a long exact sequence in Bredon cohomology:
\[\xymatrix{
	\dotsb\ar[r] & H_G^q(X;I)\ar[r] & H_G^q(X;M)\ar[r] & H_G^q(X;N\oplus L)\ar[r] & H_G^{q+1}(X;I)\ar[r] & \dotsb
}\]
Exactness at $H^q(X;N\oplus L)$ implies
\[\rank H_G^q(X;N) + \rank H_G^q(X;L) \le \rank H_G^q(X;M) + \rank H_G^{q+1}(X;I).\]
That is,
\begin{equation}
\label{1st_smith_ineq}
\rank H^q(X^G;\F_p) + \rank\wH^q((X/X^G)/G;\F_p) \le \rank H^q(X;\F_p) + \rank H_G^{q+1}(X;I).
\end{equation}
We'll use this to strongly constrain $\rank H^q(X^G;\F_p)$, but first we need another inequality coming from
another exact sequence. Namely, the following sequence of coefficient systems is exact:
\[\shortexact{L}{M}{I\oplus N}.\]
This is because $I^p = 0$ and for $0\le n\le p-1$, $I^n/I^{n+1}\cong\F_p$. In particular, $I^{p-1}\cong\F_p\cong
L$, so we can think of $M/L$ as $M/I^{p-1}$. Now we play the same game: the induced long exact sequence is
\[\xymatrix{
	\dotsb\ar[r] & H_G^q(X;L)\ar[r] & H_G^q(X;M)\ar[r] & H_G^q(X;I\oplus N)\ar[r] & H_G^{q+1}(X;L)\ar[r] & \dotsb
}\]
which implies
\[\rank H_G^q(X;N) + \rank H_G^q(X;I) \le \rank H_G^q(X;M) + \rank H_G^{q+1}(X;L),\]
i.e.
\begin{equation}
\label{2nd_smith_ineq}
\rank H^q(X^G;\F_p) + \rank H_G^q(X;I) \le \rank H^q(X;\F_p) + \rank H^{q+1}((X/X^G)/G;\F_p).
\end{equation}
Let's use this to prove
\begin{equation}
\label{3rd_smith_ineq}
\rank \wH^q((X/X^G)/G;\F_p) + \sum_{i=q}^{q+r} \rank H^i(X^G;\F_p) \le \rank\wH^{q+r+1} + \sum_{i=q}^{q+r}\rank
H^i(X;\F_p).
\end{equation}
Let
\begin{align*}
	a_q &\coloneqq \rank H^q(X^G;\F_p)\\
	b_q &\coloneqq \rank H^q(X;\F_p)\\
	c_q &\coloneqq \rank H^q((X/X^G)/G;\F_p)\\
	d_q &\coloneqq \rank H_G^q(X;I).
\end{align*}
Then, \eqref{1st_smith_ineq} and~\eqref{2nd_smith_ineq} say
\[a_q + c_q\le b_q + d_{q+1}\qquad\text{and}\qquad a_q + d_q \le b_q + c_{q+1}.\]
Now, adding~\eqref{1st_smith_ineq} for $q$ even and~\eqref{2nd_smith_ineq} for $q$ odd
proves~\eqref{3rd_smith_ineq}.
% TODO: I did not follow this in class!

When $q = 0$ and $r$ is large, the finite-dimensionality of $X$ implies that
\begin{equation}
\label{interesting_bound}
\sum_i\rank H^i(X^G;\F_p) \le \sum_i \rank H^i(X;\F_p).
\end{equation}
This is already an interesting bound, especially relative to the amount of work we've put in.

Specializing to $X$ an $\F_p$-cohomology sphere,~\eqref{interesting_bound} means
\[\sum_i \rank H^i(X^G;\F_p) \le 2.\]
We want to show this sum isn't $1$ (so that we get the cohomology of a sphere) and that the top nonzero rank is at
most $n$. We will do this with another short exact sequence of coefficient systems:
\[\shortexact{I^{n+1}}{I^n}{L}.\]
From this, we get another long exact sequence. Applying the Euler characteristic, we obtain that
\begin{equation}
\label{euler_char_ineq}
\chi(X) = \chi(X^G) + p\widetilde\chi((X/X^G)/G).
\end{equation}
Here
\[\widetilde\chi(Y)\coloneqq \sum_i (-1)^i\rank \wH^i(Y)\]
is the \term{reduced Euler characteristic}.

Equation~\ref{euler_char_ineq} already implies that $\chi(X) \equiv \chi(X^G)\bmod p$, so $\sum\rank
H^*(X^G;\F_p)\ne 1$ in our case.
\begin{comp}{ex}{enumerate}
	\item Think about choices of $q$ and $r$ that allow you to deduce $m\le n$, finishing the proof.
	\item Small changes need to be made to this argument when $p = 2$; what are they?\qedhere
\end{comp}
\end{proof}
This is an appealing proof: some fairly simple calculations and a dash of formal theory very effectively led to the
result. We'll give another proof with different advantages and disadvantages.

Smith theory naturally leads to questions about how to recover $H^*(X^G)$ algebraically from some equivariant
cohomology theory on $X$. Last time, we introduced Borel cohomology $H_G^*(X) \coloneqq H^*(EG\times_G X)$, where
$EG$ is a free $G$-space that's nonequivariantly contractible (which is simple to construct with the bar
construction or through Elmendorf's theorem).

\emph{In the following, all cohomology is understood to have coefficients in $\F_p$.} Recall that the Bredon
cohomology of $X$ is defined to be $H_G^*(X)\coloneqq H^*(EG\times_G X)$. For a subgroup $H\subset G$, let
$S_H\subset H^*(BG)$ be the multiplicative set generated by the classes in $H^2(BG)$ that are images of the
Bockstein homomorphism $H^1(BG)\to H^2(BG)$ of the elements that are nontrivial in $H^1(BH)$. This uses the fact
that Borel cohomology is an $H^*(BG)$-module: $H^*(EG\times_G *) \cong H^*(EG/G) = H^*(BG)$, and using the terminal
map $X\to *$ we get a map $H^*(BG)\to H^*(EG\times_G X)$.
\begin{thm}
\label{localization}
Let $G$ be a finite $p$-group and $H\subset G$ be a subgroup. Then, there is an isomorphism
$S_H^{-1}H_G^*(X)\stackrel\cong\to S_H^{-1}H_G^*(X^H)$.
\end{thm}

There's a rich theory of unstable modules over the Steenrod algebra $\mathcal A_p$, which could fill a whole
semester. There's a functor $\Un$ which produces unstable $\mathcal A_p$-modules, in a sense by only keeping the
unstable part.
\begin{thm}[{Dwyer-Wilkerson~\cite{SmithRevisit}}]
\[H^*(X^G) \cong \F_p\otimes_{H^*(BG)} \Un(S_G^{-1}H^*(EG\times_G X)).\]
\end{thm}
The proof uses arguments that were hard to think of, but easy to follow.

We'll use these theorems to prove Smith's theorem using the Serre spectral sequence for
\[\xymatrix{
	X\ar[r] & EG\times_G X\ar[r] & BG.
}\]
This will be the nicest kind of spectral sequence argument: everything degenerates.

Theorem~\ref{localization} is an example of a general class of \term{localization theorems} in equivariant
cohomology. In these theorems, one considers the fiber sequence $X_+^G\to X_+\to X/X^G$, and wants to show that for
some functor $E$, $E(X_+^G)\cong E(X_+)$. This boils down to showing $E(X/X^G)$ vanishes, which will always follow
from showing that $E$ vanishes on $G$-spaces whose $G$-actions are free away from the basepoint. In general, this
will reduce to considering cells, so one considers $E(G/H_+\wedge \bigvee_\alpha S^{q_\alpha})$ for some wedge of
spheres.

In our case, $E(G/H_+\wedge \bigvee_\alpha S^{q_\alpha})$ is
\[S_H^{-1} H_G^*\paren{G/H_+\wedge\bigvee_\alpha S^{q_\alpha}} = S_H^{-1} H^*\paren{EG\times_G
\paren{G/H_+\wedge\bigvee_\alpha S^{q_\alpha}}}\]
Now, the term $EG\times_G G/H\cong EG/H\cong BH$, so we have a piece that looks like $H^*(BH)$, which is how $BH$
inserts itself into the argument.
\begin{ex}
Finish the Serre spectral sequence proof of Theorem~\ref{smith}. Hint: there's a simple geometric reason why the
spectral sequence collapses, which is what makes this whole thing go.
\end{ex}
Soon we'll start talking about the stable category. As preparation for this, if you don't already know it, it's
good to remind yourself of it.

The Q\&A session will be Thursday at 8:30 PM.
